Providing A Unified User Environment for Canada’s National Advanced Computing Centers

### 2019-02-12 extended-abstract.tex
added reference for python wheels
changed year in the abstract

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
Exploiting an advanced computing platform consisting of several clusters distributed across the second-largest country in the world is challenging. Each cluster may run a different operating system, use a different generation of CPU, GPU, or network fabric, or be managed by a different team of system administrators. Presenting a unified software environment can tremendously facilitate the task of supporting researchers, but is difficult to implement. This is nevertheless what Compute Canada set out to do in 2017, in the midst of deploying a new generation of large clusters.

@@

\subsection{Packages for scripting languages}
Whenever a software package supports the installation of subpackages, as is the case with the Python, R, or Perl scripting languages, we leverage the existing package manager of that language, rather than installing subpackages as modules. In the case of Python, we are building Python wheels [11] against our software stack. Wheels are binary packages that can be installed in a matter of seconds, similar to CentOS RPM packages. Since they are built by our team, and linked against our optimize software stack, we ensure that they are both easy to installed and offer good performance.

>>>>

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
Exploiting an advanced computing platform consisting of several clusters distributed across the second-largest country in the world is challenging. Each cluster may run a different operating system, use a different generation of CPU, GPU, or network fabric, or be managed by a different team of system administrators. Presenting a unified software environment can tremendously facilitate the task of supporting researchers, but is difficult to implement. This is nevertheless what Compute Canada set out to do in 2016, in the midst of deploying a new generation of large clusters.

@@

\subsection{Packages for scripting languages}
Whenever a software package supports the installation of subpackages, as is the case with the Python, R, or Perl scripting languages, we leverage the existing package manager of that language, rather than installing subpackages as modules. In the case of Python, we are building Python wheels \cite{Wheels} against our software stack. Wheels are binary packages that can be installed in a matter of seconds, similar to CentOS RPM packages. Since they are built by our team, and linked against our optimize software stack, we ensure that they are both easy to installed and offer good performance.
